Data details

### 2023-04-20 analysis/data-details.qmd
Add map of derogations

```{r load-libraries, warning=FALSE, message=FALSE}
library(tidyverse)
library(targets)
library(DT)
library(kableExtra)
library(lubridate)

@@

# Load data 
withr::with_dir(here::here(), {
  # Final data
  tar_load(daily_panel)
})
```

@@

>>>>

```{r load-libraries, warning=FALSE, message=FALSE}
library(tidyverse)
library(targets)
library(sf)
library(DT)
library(kableExtra)
library(lubridate)

@@

# Load targets stuff
tar_config_set(store = here::here('_targets'),
               script = here::here('_targets.R'))

invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
tar_load(c(daily_panel, derogation_map_data))
```

@@

And here's a map of all the countries that derogated between January 2020 and June 2021:

```{r derogations-map, fig.width=6.5, fig.height=3.5}
ggplot() +
  geom_sf(data = derogation_map_data, aes(fill = derogations_1plus),
          linewidth = 0.1, color = "white") +
  coord_sf(crs = st_crs("+proj=robin"), datum = NA) +
  scale_fill_binned(low = colorspace::lighten(clrs[1], amount = 0.8), 
                    high = clrs[1], na.value = "grey85",
                    breaks = c(1, 4, 8, 12, 16),
                    name = "Derogations filed: ",
                    guide = guide_colorsteps(barwidth = 7, barheight = 0.4,
                                             title.vjust = 1)) +
  theme_pandem() +
  theme(panel.border = element_blank(),
        legend.title = element_text(face = "bold"),
        legend.justification = "center")
```
